Real-Time Image Recognition Using Collaborative IoT Devices

### 2018-06-11 dissemination.publication/640fb4c4b9ba9822/paper.tex
final meta updates
added instructions how to use CK snapshot from ACM DL

\begin{itemize}
  \item {\bf Algorithm:} Image recognition models of Alexnet and VGG16.
  \item {\bf Program:} Written scripts in Keras framework.
  \item {\bf Compilation:} Python $\geq$ 2.7.
  %\item {\bf Transformations: }
  \item {\bf Binary:} will be compiled on a target platform.
  \item {\bf Data set:} Randomly generated images with Numpy (thus will not be able to test accuracy).
  \item {\bf Run-time environment:} Ubuntu 16.04 ; Python version $\geq$ 2.7; Keras $\geq$ 2.1.3 with Tensorflow-gpu $\geq$ 1.5 for the backend; \emph{(for Raspberry PI systems)} Apache Avro~\cite{apache} $\geq$ 1.8.2; \emph{(for TX2 GPU)} CUDA 8.0 with cuDNN $\geq$ 5.1.
  \item {\bf Hardware:} Nvidia Jetson TX2 ; up to 11 Raspberry PI 3 with 16\,GB SD cards; power analyzer; Wifi router (we use 300Mbps, 2.4\,GHz 802.11n).
  %\item {\bf Run-time state: }
  \item {\bf Execution:} Automated via CK command line
  \item {\bf Metrics:} Inference per second; static and dynamic energy consumption.
  \item {\bf Output:} Scripts output end-to-end latency. User measures power consumption during idle state and inference operations.
  \item {\bf Experiments:} Performing inference on different hardware.
  \item {\bf How much disk space required (approximately)?}
  \item {\bf How much time is needed to prepare workflow (approximately)?}
  \item {\bf How much time is needed to complete experiments (approximately)?}
  \item {\bf Publicly available?:} Yes
  \item {\bf Code license(s)?:} 
  \item {\bf CK workflow framework used?} Yes
  \item {\bf CK workflow URL:} \url{https://github.com/ctuning/ck-request-asplos18-iot-farm}
  \item {\bf CK results URL:} \url{https://github.com/ctuning/ck-request-asplos18-results-iot-farm}
  \item {\bf Original artifact:} \url{https://github.com/parallel-ml/asplos2018-workshop}

@@

>>>>

\begin{itemize}
  \item {\bf Algorithm:} Image recognition models of Alexnet and VGG16.
  \item {\bf Program:} Written scripts in Keras framework.
  \item {\bf Compilation:} Python $\geq$ 2.7.
  %\item {\bf Transformations: }
  \item {\bf Binary:} will be compiled on a target platform.
  \item {\bf Data set:} Randomly generated images with Numpy (thus will not be able to test accuracy).
  \item {\bf Run-time environment:} Ubuntu 16.04 ; Python version $\geq$ 2.7; Keras $\geq$ 2.1.3 with Tensorflow-gpu $\geq$ 1.5 for the backend; \emph{(for Raspberry PI systems)} Apache Avro~\cite{apache} $\geq$ 1.8.2; \emph{(for TX2 GPU)} CUDA 8.0 with cuDNN $\geq$ 5.1.
  \item {\bf Hardware:} Nvidia Jetson TX2 ; up to 11 Raspberry PI 3 with 16\,GB SD cards; power analyzer; Wifi router (we use 300Mbps, 2.4\,GHz 802.11n).
  %\item {\bf Run-time state: }
  \item {\bf Execution:} Automated via CK command line
  \item {\bf Metrics:} Inference per second; static and dynamic energy consumption.
  \item {\bf Output:} Scripts output end-to-end latency. User measures power consumption during idle state and inference operations.
  \item {\bf Experiments:} Performing inference on different hardware.
  \item {\bf How much disk space required (approximately)?}
  \item {\bf How much time is needed to prepare workflow (approximately)?}
  \item {\bf How much time is needed to complete experiments (approximately)?}
  \item {\bf Publicly available?:} Yes
  \item {\bf Code license(s)?:} Apache 2.0
  \item {\bf CK workflow framework used?} Yes
  \item {\bf CK workflow URL:} \url{https://github.com/ctuning/ck-request-asplos18-iot-farm}
  \item {\bf CK results URL:} \url{https://github.com/ctuning/ck-request-asplos18-results-iot-farm}
  \item {\bf Original artifact:} \url{https://github.com/parallel-ml/asplos2018-workshop}

@@

\subsubsection{Install this CK workflow from the ACM Digital Library snapshot}

It is possible to install and test the snapshot of this workflow 
from the ACM Digital Library without interfering with your current CK installation.
Download related file "request-asplos18-artifact-?-ck-workflow.zip"
to a temporary directory, unzip it and then execute the following commands:

\begin{verbatim}
$ . ./prepare_virtual_ck.sh
$ . ./start_virtual_ck.sh
\end{verbatim}

All CK repositories will be installed in your current directory.
You can now proceed with further evaluation as described below.
